%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage{utopia}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\usepackage{hyperref}
\name{Lingyu Zhou} % Your name
\address{Ithaca, NY, 14850 $|$ 608-234-0062 $|$ lz568@cornell.edu $|$ \href{https://zhoulingyu.net}{zhoulingyu.net}} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
% \address{phone \\ website} 

\begin{document}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Univeristy of Wisconsin-Madison} \hfill { Sep 2020 - May 2023} \\
  \textit{College of Letters \& Science} \hfill {GPA: 3.898/4}
\\  {Bachelor of Science in Mathematics $|$ Data Science Certificate }

{\bf Cornell Univeristy } \hfill { Aug 2023 - Dec 2024} \\
  \textit{Master of Professional Study} %\hfill {GPA: 3.898/4}%
\\  {Applied Statistics $|$ Data Science}

%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
TOEFL &  100 (26 R + 27 L + 23 S + 24 W) \\
SAT & 1430 (640 V + 790 Q)\\
GRE & 326 (156 V/71\% + 170 Q/+98\% + 4.0 AW/54\%)
\end{tabular}


\end{rSection}


%---pub---%
\begin{rSection}{Publication}
{\bf Basic Analysis of Hog Futures Market in China (BPS\_0799), accepted by International Conference on Business and Policy Studies 
(CONF-BPS 2023)} 
\item Author: Chen Xu, \underline{\textbf{Lingyu Zhou}}, Anshi Lou, Manqi Qiu, Mengyu Cao

\item Content: This paper aims to provide an illustration and basic analysis of the characteristics and influences of the newly emerging type of 
futures in the Chinese market - hog futures and to provide a general overview of the performance of the futures under different 
circumstances. The paper also breaks down the role, impact, consequences, and brief forecasts of different types of the market from different 
perspectives and concludes with an evaluation and summary of the maturity and reliability of Chinese hog futures, which can serve as 
guidance or advice for people or organizations planning to get involved in business related to hog futures. 
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%---res---%

\begin{rSection}{Research Experience}

\begin{rSubsection}{China's Finance and Marketing Analysis Research}{Jul 2022 - Sep 2022}{Undergraduate Research, directed by Prof. Martin Cherkes (\textbf{Princeton University})}{}

\item Studied under Prof. Cherkes regarding topics of securities and market analysis. 
\item Accomplished 4 hours of meeting each week for 6 weeks for lectures. 
\item Accomplished 5-6 hours of meeting each week for 4 weeks for the paper. 
\item Wrote, organized the 40-page paper; discussed with the members to compose a paper and a final 20-minute presentation. 
\item Refined and published a 20-page academic paper about Live Hog Futures' Analysis in China. 
\end{rSubsection}

\begin{rSubsection}{DRP Research Program }{Jan 2022 - May 2022}{Undergraduate Research, directed by Jacob B Fiedler (\textbf{University of Wisconsin-Madison})}{}
\item Followed a PhD mentor's research regarding topics of Computability and Kolmogorov Complexity. 
\item 4-5 hours of reading per week; met with tutors and 2 other peers 1 hour a week for a semester. 
\item Discussed with the mentor and peers about certain problems and made presentation every week. 
\item Accomplished a 15-minute defense presentation at the end of semester.   
\end{rSubsection}

\begin{rSubsection}{Innovative Wireless Sensor Networks' Application on Network \\and Routing Safety}{May 2018 - July 2021}{Innovation project and  patent, directed by Hang Shen (\textbf{Nanjing Tech University})}{}
\item Gained knowledge about network safety and Wireless Sensor Networks and subsidiary technologies 
such as Bluetooth, NFC and Zigbee. 
\item Discuss problem arose during experiments and projects with team members regularly.
\item Gained research experiences and scientific study and experimental method 

\item Successfully applied for a patent (N201811148566).  
\end{rSubsection}
\end{rSection}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{INTERNSHIP EXPERIENCES}

\begin{rSubsection}{Shanghai SINO Environmental Technology Co., Ltd,}{May 2021 - May 2022}{Data Analysist Intern}{Shanghai, China \& Remote}
\item Review, supervise and process data from environmental monitoring.
\item  Sort, classify and arrange the processed data using Excel and Python. 
\item  Analyze and research data according to specific scenarios, analyze possible problems and report timely.
\end{rSubsection}

\begin{rSubsection}{Division of University Housing, University of Wisconsin-Madison}{Sep 2022 - Dec 2022}{Dining \& Culinary Services Team Member}{Madison, WI}
\item  Work with other students and professional staff to finish culinary and food prep work. 
\item  Operate cash register/POS system. 
\item  Maintaining a sanitary and inviting dining and working area. 
\item  Serve hot and cold menu items; grill; stock and inventory food and supplies. 
\end{rSubsection}


\begin{rSubsection}{Jiangsu HopeRun Software Co., Ltd.}{July 2023 - Aug 2023}{Assistant to Strategic Tech. Dept.}{Nanjing, China}

\item Study about Apache Flink, including core concepts, structure, the deployment of the platform in the local WLS, use, task submission, and analysis of the results.


\item Use Linux commands  TCP/IP, HTTP, netcat, etc to deploy the WSL and MQTT environment for Apache Flink  
\item Use MQTT and various Apache Flink's APIs in Java to process batch data, stream data simulated by netcat and MQTT in Apache Flink.

% \item Learned the operation principle, communication protocol, connection and usage of MQTT.

\item Study about the specific process, underlying framework and logic of market research and apply them to participate in the market research of China's smart healthcare market and the production of the research report PowerPoint.


\end{rSubsection}
\end{rSection}
%---???---%


\begin{rSection}{PROFESSIONAL SKILLS }

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Skills & Python, Java, Stata, C++, Visual Basic, HTML, R, SAS \\
Software \& Tools & \LaTeX, Microsoft Office, SSH, PowerShell, WordPress, Linux\\ &  Adobe Premiere, Adobe Photoshop, SQL, Blender \\
Languages & Mandarin (Native), English (Bilingual), Korean (Decent) 
\end{tabular}

\end{rSection}

%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Academic Achievements} \itemsep -2pt
\item Distinction of top 15\% distinction in CEMC(12)
\item 2020-2021 Dean's list (University of Wisconsin-Madison)
\item 2021-2022 Dean's list (University of Wisconsin-Madison)
\item 2022-2023 Dean's list (University of Wisconsin-Madison)
\item Distinctive Scholastic Achievement (University of Wisconsin-Madison)
\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Relevant Courses}
\itab{\textbf{Core Courses}} \tab{}  \tab{\textbf{Other Courses}}
\\ \itab{Multivariable Calculus} \tab{}  \tab{Data Science Software Engineering} 
\\ \itab{Advanced Linear Algebra \& Differential Equations} \tab{}  \tab{Data Programming: Python}
\\ \itab{Nonlinear Dynamics \& Chaos} \tab{}  \tab{Programming: Java} 
\\ \itab{Mathematical Analysis} \tab{} \tab{Advanced Econometrics}
\\ \itab{Mathematical Methods in Data Science} \tab{} \tab{Micro/Macro economy}
\\ \itab{Probability and Statistics Theory} \tab{}  \tab{International Trade} 
% \\ \itab{Process Control (ongoing)} \tab{} \tab{Electrodynamics}

\end{rSection}



%------------------------------------------------


%----------------------------------------------------------------------------------------
\begin{rSection}{Membership} \itemsep -3pt
\item UW-Madison Badminton Club \hfill{Sep 2022 - Dec 2022}
\item UW-Madison Korean "Happy Hour" Club \hfill{Jan 2023 - May 2023}
\end{rSection}

\end{document}
